%% start of file `template.tex'.
%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2013 Jorge Martinez Lopez (jorgeml@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}    % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                  % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}           % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}      % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\firstname{Jorge}
\familyname{Martínez~López}
\title{Telecommunications Professional}                          % optional, remove / comment the line if not wanted
\address{London}{United Kingdom}    % optional, remove / comment the line if not wanted
\mobile{+447414861067}                     % optional, remove / comment the line if not wanted
%\phone{+2~(345)~678~901}                      % optional, remove / comment the line if not wanted
%\fax{+3~(456)~789~012}                        % optional, remove / comment the line if not wanted
\email{jorgeml@jorgeml.net}                          % optional, remove / comment the line if not wanted
\homepage{about.me/jorgeml}                    % optional, remove / comment the line if not wanted
%\extrainfo{additional information}            % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                  % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                            % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Experience}
\subsection{Professional Experience}
\cventry{2009--2012}{Technical Project Manager}{Alcatel-Lucent}{the Netherlands}{}{Three years experience as a consultant in the Global Customer Delivery team in the Benelux.\newline{}%
Detailed achievements:%
\begin{itemize}%
\item During the last year was System Integrator Lead for three large projects in the IMS Solution Integration Office for a large Dutch wire-line operator:
  \begin{itemize}
  \item Supervised a Technical Project Manager in each project, overseeing schedules and resource planning on all three projects and liaising with the other leads.
  \item Led pre-sales support by providing requirements definition and commercial offers for the three projects. Offer definition included in-house hardware and services plus third party resources.
  \item Responsible for vendor management within each project (up to 3 vendors per project), including vendor compliance, offer management and regular project activities.
  \item Mentoring activities and on the job training for two new hires for almost six months. 
  \end{itemize}
\item Previously worked two years as tool specialist consultant in a managed services project for a Belgian 2G/3G mobile operator:
\begin{itemize}
  \item Responsible for the Operations Support Systems (OSS) tooling (BMC Remedy ticketing, Netcool alarms) for both incident management and new requests to the service provider.
  \item Involved in ITIL-based Operations and Rollout processes design, implementation and improvement.
  \item Supported integration activities providing input to the project team with respect to tools and processes.
  \item Responsible of the delivery and agreement with the customer of 100+ operational reports (including KPIs). 
  \item Contributed to the disaster recovery plan and co-authored the exit plan.
\end{itemize}  
\end{itemize}}
\cventry{2008}{Research \& Development Intern}{Smart Signs Solutions}{the Netherlands}{}{Worked part-time a few months to finance a study trip to Japan.\newline{}
Detailed achievements:%
\begin{itemize}
\item Development of guest detection functionality using RFID in a smart wayfinding
platform.
\item Customized deployment of a Linux distribution specific for low computing power devices. 
\item Investigation and resolution of wireless networking issues.
\end{itemize}
}
\cventry{2006}{Innovation Department Intern}{Bankinter}{Madrid, Spain}{}{Second-line technical support of the mobile applications developed by the bank: mobile banking and stock trading.\newline{}
Wrote documentation for the first-line of support team.}


%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description}

\subsection{Volunteer Experience}
\cventry{2004--2007}{Local Section Member}{Erasmus Student Network}{}{}
{
\begin{itemize}
\item Joined ESN Carlos III (Madrid, Spain) and afterwards ESN Twente (Enschede, the Netherlands) during my studies.
\item Organized local, national and international events and activities.
\item Mentored incoming international students.
\item Promoted the Socrates/Erasmus internship by providing information and advice to prospective students.
\item Collaborated with university management.
\end{itemize}
}
\cventry{2006--2007}{WebTeam Member}{Erasmus Student Network}{}{}
{
\begin{itemize}
\item Contributed to the development and deployment of a local section website template based on Drupal.
\end{itemize}
}
\cventry{2006--2007}{Council of National Representatives, Spain's ViceNational Representative}{Erasmus Student Network}{}{}
{
\begin{itemize}
\item Represented the Spanish sections at the international meetings.
\end{itemize}
}


\section{Education and Training}
\subsection{Certifications}
\cventry{2009}{Foundation Certificate in Software Testing (ISTQB)}{Information Systems Examinations Board (ISEB)}{}{}{}  % arguments 3 to 6 can be left empty
\subsection{Courses}
\cventry{2013}{Think Again: How to Reason and Argue}{Duke University}{Coursera}{}{}
\subsection{Degrees}
\cventry{2008}{M.Sc. in Telematics}{University of Twente}{Enschede, the Netherlands}{}{Thesis in ``Dynamic Service Composition in an Innovative Communication Environment''.\newline{}
``Bonsai'' Study Tour to Japan in February 2008, topic ``Smart Surroundings''.}
\cventry{2008}{Degree in Telecommunications Engineering}{Universidad Carlos III de Madrid}{Madrid, Spain}{}{Majored in ``Planning and
Management of Telecommunications'', including management courses not specific to telecommunications, such as business administration, human resources, quality management and innovation.
\newline{}Socrates/Erasmus student exchange program at the University of Twente from September 2003 to March 2004.}
\subsection{Master thesis}
\cvitem{title}{\emph{Dynamic Service Composition in an Innovative Communication Environment'' (EU FP6 SPICE)}}
\cvitem{supervisors}{L.~Ferreira Pires, M.~van Sinderen, E.M.~Gon\c{c}alves da Silva}
\cvitem{description}{Dynamic Service Composition enables the creation and delivery of new customised and attentive services to the end-user upon a service request, at run-time. These new services are made by composing already existing ones.}


\section{Languages}
\cvitemwithcomment{Spanish}{Native}{}
\cvitemwithcomment{English}{Full professional proficiency}{}
\cvitemwithcomment{Dutch}{Professional working proficiency}{}

%\section{Computer skills}
%\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

\section{Interests}
\cvitem{Basketball}{Played at the University and at a regional league in the Netherlands.}
\cvitem{Free software}{Linux user, I contribute by reporting bugs, participating in mailing lists, etc.}
\cvitem{Travelling}{Visited many countries, mostly within Europe.}
\cvitem{Photography}{Point-and-shoot, looking forward to buy a DSLR.}

\section{Awards}
\cvlistitem{Alcatel-Lucent's ``A Night Out'' for the outstanding effort in the Belgian mobile operator project.}
\cvlistitem{Erasmus Student Network Alumnus (Honorary life-time membership) for my contribution during a period of three years in two local sections. Participated and sometimes organized national and international events (workshops, meetings\ldots). Served as Vice-National Representative for Spain for a year.}

\section{Additional information}
\cvlistitem{LinkedIn profile available at \url{http://uk.linkedin.com/in/jorgeml}.}
\cvlistitem{Latest version of this résumé available at \url{https://github.com/jorgeml/resume/raw/master/resume.pdf}.}

%\renewcommand{\listitemsymbol}{-~}            % change the symbol for lists

%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
%\cvlistdoubleitem{Item 3}{}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                   % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}              % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}              % 'publications' is the name of a BibTeX file

\clearpage
%-----       letter       ---------------------------------------------------------
% recipient data
% \recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
% \date{\today}
% \opening{Dear Sir or Madam,}
% \closing{Yours faithfully,}
% \enclosure[Attached]{curriculum vit\ae{}}     % use an optional argument to use a string other than "Enclosure", or redefine \enclname
% \makelettertitle
% I am applying for the XXXXXXXX opportunity at XXXXXXXX as advertised on XXXXXXXX. This position may fit very well with my education, experience and career interests and I am confident that I can perform the job effectively. 
%
% I am a Telecommunications professional with more than three years of work experience. In my previous role I worked as System Integration Lead (Technical Project Manager and Presales support) for the solution integration team for a Dutch telecommunications operator, leading projects that introduced new services in a complex VoIP (IMS) telecommunications network. Previously I worked as a project consultant in managed services for a mobile operator in Belgium. My activities included participating in the design and implementation of ITIL processes, taking the responsibility of delivering operational reports to the customer (including KPIs), supporting to the integration projects and, during the last months in the project, I was solely responsible of the communication with the Operations Support tooling service provider.
% 
% I have excellent communication skills and I am used to deal with a variety of people on different levels (team, peers, customers, suppliers and all levels of management). My mother tongue is Spanish, I am fluent in English and I have a good level of Dutch.
% I am certified in software testing (ISTQB Foundation level).
% I enjoy sharing my knowledge with others and I am always looking forward to learning new things.
% 
% Through my work experience, I have developed some key strengths for success in this role including:
% \begin{itemize}
% \item Passion for technology.
% \item Teamwork, willingness to help and be helped.
% \item Inter-cultural skills gained living abroad and being member of an international student organization.
% \item Strong customer focus developed in a high-demanding managed services project.
% \end{itemize}
%  
% My résumé provides additional information on my education and experience. 
% 
% I would appreciate the opportunity to discuss my background and qualifications with you in further detail.
% 
% Thank you for your time and consideration. I look forward to hearing from you soon.
% 
% \makeletterclosing

\end{document}


%% end of file `template.tex'.
